Appendix 1: Quantifying Drought

### 2021-05-06 doc/SPEI_appendix.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = FALSE,
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.path = "figures/",
  dpi = 300)
source(here::here("packages.R"))
```

*Last compiled: `r Sys.Date()`* \# TODO

-   Write brief text
-   Possibly make a figure S2 that compares SPEI across BDFFP from east to west (3 panels), using all data with similar resolution

@@

```{r spei-table, fig.cap=cap}
# knitr::include_graphics(here("analysis", "supplementary-materials", "spei_table.png"))
table
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = FALSE,
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.path = "figures/",
  dpi = 300)
source(here::here("packages.R"))
source(here::here("R", "utils.R"))
```

*Last compiled: `r Sys.Date()`*

# TODO

-   Write brief text
-   Convert table to `kableExtra` so it knits in word and pdf

@@

```{r spei-table, fig.cap=cap}
# knitr::include_graphics(here("analysis", "supplementary-materials", "spei_table.png"))
table #only works when knit to HTML
```
